DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-02-01 paper/overview.tex
..

Note that although the steering angle output of the network $angle$ is
a continuous real value, the RC car platform we used unfortunately
only supports three discrete angles---left (-30$^{\circ}$), center
(0$^{\circ}$), and right (+30$^{\circ}$)---as control inputs.
Currently, we approximate the network generated real-valued
angle to the closest one of the three angles, which may
introduce inaccuracy in control.
In the future, we plan to use a different (more expensive) RC car
platform that can precisely control the car's steering angle.
We would like to stress, however, that the use of different RC car
platforms has no impact on the computational 
aspects of the system, and that our main focus of this study is
not in improving network accuracy but in closely replicating the
DAVE-2's network architecture and its real-time characteristics.

@@

>>>>

Note that although the steering angle output of the network $angle$ is
a continuous real value, the RC car platform we used unfortunately
only supports three discrete angles---left (-30$^{\circ}$), center
(0$^{\circ}$), and right (+30$^{\circ}$)---as control inputs.
Currently, we approximate the network generated real-valued
angle to the closest one of the three angles, which may
introduce inaccuracy in control.
In the future, we plan to use a different (more expensive) RC car
platform that can precisely control the car's steering angle.

@@

We would like to stress, however, that the the issues related to the
CNN's accuracies have no impact on the \emph{computational 
aspects of the system}, and that our main focus of this study is
not in improving network accuracy but in closely replicating the
DAVE-2's network architecture and studying its real-time
characteristics.
